Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-18 paper/main.tex
Replace pareto_mae_nofit_PNAS with mae_nofit generated by modeleval_rsi21.m
Replace eq_goodbad_PNAS with individual subfigures generated by forcesim_rsi21.m

\begin{figure}%[!htb]
\centering
\begin{subfigure}{0.3\textwidth}
\includegraphics[trim=0 15 0 5, clip, width=\textwidth]{figures/apparatus}
\caption{\label{fig:apparatus}}
\end{subfigure}
\qquad
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/pareto_mae_nofit_PNAS}
\caption{\label{fig:pareto_mae}}
\end{subfigure}
\caption{\subref{fig:apparatus} Schematic diagram of the experimental apparatus showing three
  kinematic variables of the wing motion: stroke ($\phi$), deflection ($\psi$) and deviation
  ($\theta$). \subref{fig:pareto_mae} Pareto plot of all data-driven (``EQ Models'') and analytical
  models using mean values for model coefficients. All data-driven models were smaller and more
  accurate than analytical models.
}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{figures/eq_goodbad_PNAS}
\caption{Comparison of force predictions between $EQ_4$ (blue) and Equation~\eqref{eq:badeq} (red).
  $EQ_4$ was trained on 58 distinct experiments simultaneously, including the data shown in (A),
  whereas Equation~\eqref{eq:badeq} was trained \emph{only} on the data shown in (A).  Panel (A)
  shows that both models perform well on this data within their training sets.  However, when
  presented with data outside their training set (B,C,D), only $EQ_4$ is able to generalize and
  provide accurate predictions, while Equation~\eqref{eq:badeq} fails to do so.}
\label{fig:eq_goodbad}
\end{figure}

>>>>

\begin{figure}%[!htb]
\centering
\begin{subfigure}{0.3\textwidth}
\includegraphics[trim=0 15 0 5, clip, width=\textwidth]{figures/apparatus}
\caption{\label{fig:apparatus}}
\end{subfigure}
\qquad
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/mae_nofit}
\caption{\label{fig:pareto_mae}}
\end{subfigure}
\caption{\subref{fig:apparatus} Schematic diagram of the experimental apparatus showing three
  kinematic variables of the wing motion: stroke ($\phi$), deflection ($\psi$) and deviation
  ($\theta$). \subref{fig:pareto_mae} Pareto plot of all data-driven (``EQ Models'') and analytical
  models using mean values for model coefficients. All data-driven models were smaller and more
  accurate than analytical models.
}
\end{figure}

@@

\begin{figure}[ht]
\centering
\begin{tabular}{cc}
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/eq_goodbad_1}
\caption{\label{fig:eq_goodbad_1}}
\end{subfigure} &
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/eq_goodbad_2}
\caption{\label{fig:eq_goodbad_2}}
\end{subfigure} \\
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/eq_goodbad_3}
\caption{\label{fig:eq_goodbad_3}}
\end{subfigure} &
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/eq_goodbad_4}
\caption{\label{fig:eq_goodbad_4}}
\end{subfigure}
\end{tabular}
\caption{Comparison of force predictions between $EQ_4$ (blue) and
Equation~\eqref{eq:badeq} (red). $EQ_4$ was trained on 58 distinct experiments
simultaneously, including the data shown in~\subref{fig:eq_goodbad_1}, whereas
Equation~\eqref{eq:badeq} was trained \emph{only} on the data shown
in~\subref{fig:eq_goodbad_1}.  \subref{fig:eq_goodbad_1} shows that both models
perform well on this data within their training sets.  However, when presented
with test data \subref{fig:eq_goodbad_2}, \subref{fig:eq_goodbad_3} and
\subref{fig:eq_goodbad_4} not contained within either model's training set, only $EQ_4$ is able to
generalize and provide accurate predictions, while Equation~\eqref{eq:badeq}
fails to do so.}
\label{fig:eq_goodbad}
\end{figure}
